Temporal stability in human interaction networks

### 2015-11-02 paper.tex
pequeno retoque e anotacao

\subsection{Types from Erd\"os sectors}\label{sec:pty}
Assigning a type to a participant raises important 
issues about the scientific cannon for human types
and the potential for stigmatization and prejudice. 
The type of the Erd\"os sector to which a participant belongs 
can be regarded as implying a social type to the corresponding participant.
In this case, the type of a participant
changes both along time and as
different networks are considered,
despite the stability of the network,
and therefore the potential for prejudice of such
participant typology is attenuated~\cite{adorno}. 
In other words, an individual is a hub in a number of networks and peripheral in other networks,
and even within the same network he/she most probably changes type along time~\cite{animacoes}.

@@

@@

Further work should expand the analysis to include
more types of networks and more metrics.
The data and software needed to attain these results
should also receive dedicated and in-depth
documentation as they enable a greater level of transparency
and work share,
which is adequate for both benchmarking
and specifically for the study of systems constituted
by human individuals (see Section~\ref{sec:data}).
The derived typology of hub, intermediary and peripheral participants
has been applied for semantic web and participatory democracy efforts,
and these developments might be enhanced to yield scientific knowledge~\cite{opa}.
Also, we plan to further apply and publish of the visualization and sonification
processes used for this research~\cite{versinus,animacoes} and
the extreme linguistic differences found in each of the Erd\"os sectors~\cite{rcText}.

@@

\begin{acknowledgments}
	Financial support was obtained from CNPq (140860/2013-4,
	project 870336/1997-5), United Nations Development Program (contract: 2013/000566; project BRA/12/018) and FAPESP. 
	The authors are grateful to the American Jewish Committee for maintaining an online copy of the Adorno book used on the epigraph~\cite{adorno}, to Gmane creators and maintainers for the public email list data, to the communities of the email lists and other groups used in the analysis, and to the Brazilian Presidency of the Republic for keeping Participabr code and data open.
	We are also grateful to developers and users of Python scientific tools.
\end{acknowledgments}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\nocite{*}
\bibliography{paper}% Produces the bibliography via BibTeX.

>>>>

\subsection{Types from Erd\"os sectors}\label{sec:pty}

Assigning a type to a participant raises important 
issues about the scientific cannon for human types
and the potential for stigmatization and prejudice. 
The type of the Erd\"os sector to which a participant belongs 
can be regarded as implying a social type to the corresponding participant.
In this case, the type of a participant
changes both along time and as
different networks are considered,
despite the stability of the network,
and therefore the potential for prejudice of such
participant typology is attenuated~\cite{adorno}. 
In other words, an individual is a hub in a number of networks and peripheral in other networks,
and even within the same network he/she most probably changes type along time~\cite{animacoes}.

@@

\section{Discussion}
% given the results, and before reaching the conclusions
% what to say?
% --> what is the overall knowledge derived from the results
% --> what are the limitations of this knowledge and of individual results
% --> how should this results carry on is on the next sections.
\subsection{Consecutive scientific research}
% --> research
% textual diferences
% audiovisualization of data
% typologies, sociological critical theory, social psychology

\subsection{Technological applications}
% --> technological 
% resources categorization and recommendation
% document creation
% ontologies for the semantic web

\subsection{Experimental and theoretical aspects of the research}
% --> methods
% Exploratory?
% Hypothesis testing?
% --> contributions
% verifiable
% knowledge
% contextualization in the academic knowledge

% applications 
% experimental and theoretical aspects of the research

@@

Further work should expand the analysis to include
more types of networks and more metrics.
The data and software needed to attain these results
should also receive dedicated and in-depth
documentation as they enable a greater level of transparency
and work share,
which is adequate for both benchmarking
and specifically for the study of systems constituted
by human individuals (see Section~\ref{sec:data}).
The derived typology of hub, intermediary and peripheral participants
has been applied for semantic web and participatory democracy efforts,
and these developments might be enhanced to yield scientific knowledge~\cite{opa}.
Also, we plan to further explore and publish of the visualization and sonification
processes used for this research~\cite{versinus,animacoes} and
the extreme linguistic differences found in each of the Erd\"os sectors~\cite{rcText}.

@@

\begin{acknowledgments}
	Financial support was obtained from CNPq (140860/2013-4,
	project 870336/1997-5), United Nations Development Program (contract: 2013/000566; project BRA/12/018) and FAPESP. 
	The authors are grateful to the American Jewish Committee for maintaining an online copy of the Adorno book used on the epigraph~\cite{adorno}, to Gmane creators and maintainers for the public email list data, to the communities of the email lists and other groups used in the analysis, and to the Presidency of the Brazilian Republic for keeping Participabr code and data open.
	We are also grateful to developers and users of Python scientific tools.
\end{acknowledgments}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\nocite{*}
\bibliography{paper}% Produces the bibliography via BibTeX.
